My title

### 2022-04-06 outputs/paper/paper.Rmd
update to paper

library(tidyverse)
library(palmerpenguins)
library(scales)

data <- readr::read_csv("../data/cleaned_data.csv")
```

@@

```{r bills, fig.cap="Bills of penguins", echo = FALSE,fig.width=8, fig.height=4}
age_group_diverging <- data %>%
  filter(demographic_type == "age group", survey_answer != "don't know") %>%
  mutate(chances_of_getting_aids = if_else(survey_answer %in% c("no risk at all", "small"), -chances_of_getting_aids, chances_of_getting_aids)) %>%
  mutate(percent_label = abs(chances_of_getting_aids)) %>%
  mutate(percent_label = percent(chances_of_getting_aids / 100, accuracy = 1))

@@

# Results

>>>>

library(tidyverse)
library(palmerpenguins)
library(scales)
library(broom)

data <- readr::read_csv("../data/cleaned_data.csv")
data <- data %>%
  filter(demographic_info != "Don’t know/missing", survey_answer != "don't know")
```

@@

```{r bills, fig.cap="Bills of penguins", echo = FALSE,fig.width=8, fig.height=4}
age_group_diverging <- data %>%
  filter(demographic_type == "age group") %>%
  mutate(chances_of_getting_aids = if_else(survey_answer %in% c("no risk at all", "small"), -chances_of_getting_aids, chances_of_getting_aids)) %>%
  mutate(percent_label = abs(chances_of_getting_aids)) %>%
  mutate(percent_label = percent(chances_of_getting_aids / 100, accuracy = 1))

@@

```{r f, echo = FALSE, warning=FALSE}
data1 <- data %>% filter( demographic_type == "age group")

scatterPlot1 <- ggplot(data1, aes(demographic_info, chances_of_getting_aids, color = survey_answer)) +
  geom_point() + geom_jitter()+ facet_wrap(~gender)+
  stat_smooth(aes(group = survey_answer), method = "loess", se = FALSE, lty='dashed') +
  labs(
    title = "Survey Respondent Distribution",
    x = "age group",
    y = "survey respondents",
    fill = NULL
  )+scale_color_brewer(
    palette="Spectral")+
  theme_minimal()
scatterPlot1
```
# Results
